Stabilization-Free Virtual Element Methods

### 2023-03-14 stabfreevem_sinum.tex
proofread

% REQUIRED
\begin{abstract}
Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these stabilization-free virtual element methods. Numerical results are provided to verify the convergence rates.
\end{abstract}

@@

\section{Introduction}
\XH{A stabilization term is usually required in the virtual element methods (VEM) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems. The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
The stabilization term appears in both side of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
}

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}. 
\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. \XH{By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.}

@@

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

By the aid of projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming virtual element method in arbitrary dimension and a stabilization-free conforming virtual element method in two dimensions  for second order elliptic problems.
Indeed, these stabilization-free virtual element methods can be equivalently recast as
primal mixed virtual element methods.
We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free virtual element methods, and derive the optimal error estimates.

The idea on constructing stabilization-free virtual element methods in this paper is simple,
and can be extended to more virtual element methods and more partial differential equations.

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a Banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$ being the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

For a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ be the unit outward normal vector to $\partial K$, which will be abbreviate as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

For a $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.

@@

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On the face $F\in\mathcal F_h$, define surface divergence
\[
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
\]
For a smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

@@

For $K\in \mathcal T_h$, let $\boldsymbol{x}_K$ be the center of  the largest ball contained in $K$.
Throughout this paper, we use
``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
which may take different values at different appearances. And $A\eqsim B$ means $A\lesssim B$ and $B\lesssim A$.

@@

\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x},
\end{equation}
\XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

@@

For $\boldsymbol{v}\in\mathbb P_{k-1}(T;\mathbb R^d)\cap\ker(\skw\nabla)$, by decomposition \eqref{eq:Pkvectordecomp}, there exist $q\in \mathbb P_k(T)$ and $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ such that $\boldsymbol{v}=\nabla q+\boldsymbol{w}$. 
By $\skw\nabla\boldsymbol{v}=\boldsymbol{0}$, we get $\skw\nabla\boldsymbol{w}=\boldsymbol{0}$. 
Apply Lemma~\ref{lem:skwgrad} to derive $\boldsymbol{w}=\boldsymbol{0}$. Thus $\boldsymbol{v}=\nabla q\in\nabla\mathbb P_k(T)$.
\end{proof}

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big),
\end{equation}
where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})$ means the kernel of operator $\boldsymbol{x}: \mathbb P_{k-2}(T;\mathbb K)\to\mathbb P_{k-1}(T;\mathbb R^d)$.
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
\[
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
\]
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
\[
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
\]
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

Now let $w\in H^1(K)/\mathbb R$ be the solution of 

@@

(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.

@@

Finally \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.

@@

For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, and the $L^2$ projection
\begin{equation}\label{eq:QKPik}  
Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv
\end{equation}
is also computable using only DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}.

>>>>

% REQUIRED
\begin{abstract}
Stabilization-free virtual element methods (VEMs) in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these stabilization-free VEMs. Numerical experiments are provided to test the stabilization-free VEMs.
\end{abstract}

@@

\section{Introduction}
\XH{A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems. The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
}

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}. 
\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. \XH{By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.}

@@

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require that
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for the space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

By the aid of the projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming VEM in arbitrary dimension and a stabilization-free conforming VEM in two dimensions  for second order elliptic problems.
Indeed, these stabilization-free VEMs can be equivalently recast as
primal mixed VEMs.
We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free VEMs, and derive the optimal error estimates. Numerical experiments are provided to test these VEMs.

The idea on constructing stabilization-free VEMs in this paper is simple,
and can be extended to more VEMs and more partial differential equations.

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming VEM in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming VEM in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a Banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$ being the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
Let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of a tensor $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

Given a $d$-dimensional polytope $K$, let $\mathcal{F}(K)$ and $\mathcal{E}(K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of $K$ respectively. For $F\in\mathcal{F}(K)$, denote by $\boldsymbol{n}_{K,F}$ the unit outward normal vector to $\partial K$, which will be abbreviated as $\boldsymbol{n}_F$ or $\boldsymbol{n}$ if not causing any confusion.

Given a $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of the point $\boldsymbol x$ corresponding to the vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.

@@

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For a smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On the face $F\in\mathcal F_h$, define the surface divergence
\[
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
\]
Define the surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$ for a smooth function $v$.

@@

For $K\in \mathcal T_h$, let $\boldsymbol{x}_K$ be the center of  the largest ball contained in $K$.
Throughout this paper, we use
``$\lesssim\cdots $" to mean that ``$\leq C\cdots$", where
$C$ is a generic positive constant independent of mesh size $h$, but may depend on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$,
which may take different values at different appearances. Let $A\eqsim B$ mean $A\lesssim B$ and $B\lesssim A$.

@@

\subsection{$H(\div)$-conforming finite elements}
For a $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, \XH{and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable}.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}
% \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

@@

For $\boldsymbol{v}\in\mathbb P_{k-1}(T;\mathbb R^d)\cap\ker(\skw\nabla)$, by decomposition \eqref{eq:Pkvectordecomp}, there exist $q\in \mathbb P_k(T)$ and $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ such that $\boldsymbol{v}=\nabla q+\boldsymbol{w}$. 
By $\skw\nabla\boldsymbol{v}=\boldsymbol{0}$, we get $\skw\nabla\boldsymbol{w}=\boldsymbol{0}$. 
Apply Lemma~\ref{lem:skwgrad} to derive $\boldsymbol{w}=\boldsymbol{0}$. Thus, $\boldsymbol{v}=\nabla q\in\nabla\mathbb P_k(T)$.
\end{proof}

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big),
\end{equation}
where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x}):=\{\boldsymbol{\tau}\in\mathbb P_{k-2}(T;\mathbb K): \boldsymbol{\tau}\boldsymbol{x}=\boldsymbol{0}\}$.
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
\[
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
\]
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
\[
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
\]
Hence, $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

Now let $w\in H^1(K)\cap L_0^2(K)$ be the solution of 

@@

(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)\cap L_0^2(K).

@@

Finally, \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.

@@

For $v\in V_k(K)$, the $H^1$ projection $\Pi_k^Kv$ is computable using DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}, and the $L^2$ projection
\begin{equation}\label{eq:QKPik}  
Q_k^Kv= \Pi_k^Kv + Q_{k-2}^Kv-Q_{k-2}^K\Pi_k^Kv
\end{equation}
is also computable using DoFs \eqref{eq:vemdof1}-\eqref{eq:vemdof2}.
